2H qSIP Calculations

### 2021-11-08 qSIP_calculations.Rmd
added weighted turnover

# Load packages

@@

# Turnover Calculation Function

@@

gen_calc_data_summarized <- peaks_mapped_summarized %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )

>>>>

# Load packages and functions

@@

## Turnover Calculation Function

@@

gen_calc_data_summarized <- peaks_mapped_summarized %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time (d)
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d),
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )

weighted_turnover_summarized <- gen_calc_data_summarized %>% 
  group_by(terrain, inc_time_d) %>%
  summarize(u_d_weighted = sum(u_d * rel_area_FID, na.rm = TRUE) / sum(rel_area_FID, na.rm = TRUE))

gen_calc_data_summarized <- left_join(gen_calc_data_summarized, 
                                     weighted_turnover_summarized,
                                     by = c("terrain", "inc_time_d"))
